### 2012-03-21 intention motor representation with corrado sinigaglia/intention and motor action.ppr.r1.tex
intention motor representation r1 before check

\def \ititle {Intention and motor representation:}
\def \isubtitle {how to resist temptation}
\def \iauthor {S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

\section{A motor format for representation}

The second temptation is to suppose that motor representation, or some species of it, is a variety of intention, where intention is understood in the standard way as a propositional attitude with a characteristic role in practical reasoning \citep{Bratman:1987xw}. In this section we explain why this temptation should also be resisted.

As background we first need a generic distinction between content and format. Imagine you are in an unfamiliar city and are trying to get to the central station. A stranger offers you two routes. Each route could be represented by a distinct line on a paper map. The difference between the two lines is a difference in content. Each of the routes could alternatively have been represented by a distinct series of instructions written on the same piece of paper; these cartographic and propositional representations differ in format. The format of a representation constrains its possible contents. For example, a representation with a cartographic format cannot represent what is represented by sentences such as `There could not be a mountain whose summit is inaccessible.'\footnote{ Note that the distinction between content and format is orthogonal to issues about representational medium. The maps in our illustration may be paper map or electronic maps, and the instructions may be spoken, signed or written. This difference is one of medium.} The distinction between content and format is necessary because, as our illustration shows, each can be varied independently of the other.

Our aim in this section is to show that motor representations differ from intentions with respect to their format. This is why the second temptation must be resisted. That motor representations differ in format from intentions shows that they are genuinely distinct phenomena.\footnote{ Readers already convinced that motor representation differs from intention in being non-conceptual will not need the following argument in order to conclude that they are distinct phenomena. However the following considerations also show that motor and perceptual representations differ in format, which will be relevant in later when we consider how motor representations and intentions jointly lead to action.}

How can we distinguish representational formats? Because a representational format is typically associated with characteristic processing profiles, it is sometimes possible to infer similarities and differences in representational format from similarities and differences in the processes in which representations feature. This works both for artifactual and mental representations.  To illustrate in terms of our earlier example, suppose that two people have representations of the same route but for one person the route is represented by a line on a map (so in a cartographic format) whereas the other person has a propositional representation of the route. Some transformations are likely to be easier for the person with the cartographic route representation (depending on the projection used, of course); examples include reversing the route, determining how many times a certain river is crossed and transforming the route into a sequence of compass bearings. Other transformations, such as turning the route into a list of salient landmarks, may be easier for the person with the propositional route description. So some patterns of difference in the two people's performances may be explained by the difference in the formats of their representations. If we did not already know that the two people's route representations involved different formats, we might infer this from the facility with which each performed various transformations of the route.

Cognitive neuroscience frequently depends on inferences of just this type. Contrast imagining seeing an object moving with imagining moving an object. There is evidence that imagining seeing and imagining acting involve different processes. For instance, each can be selectively impaired \citep{sirigu:2011_motor}; and factors such as limb amputation or hand posture can selectively interfere with imagining performing an action \citep{nico:2004_left,vargas:2004s_influence,fourkas:2006_influence}. Importantly for our purposes, imagining seeing an object move and imagining moving an object also differ in ways that indicate differences in representational format. For instance, the way imagining acting unfolds in time is quite different from the way imagining seeing unfolds: how long the former takes is closely related to the time it would take to perform the action, but this is not true of the latter \citep{decety:1989_timing,decety:1996_imagined,Jeannerod:1994oz}. In addition, for object-related actions such as grasping the handle of a cup, manipulating the object in ways that make the action harder (such as orienting the handle to make it less convenient for you to grasp) make a corresponding difference to the effort involved in imagining performing the action \citep{parsons:1994_temporal,frak:2001_orientation}, whereas such manipulations would make no systematic difference to the effort involving in imaging seeing. The explanation for these differences between imagining acting and imagining seeing plausibly involves a difference in the formats of the representations involved.

How do these findings bear on motor representation? Contrast imagining an action with actually performing that action. There is substantial evidence that imagining an action involves many of the same processes which would be involved in performing that action up to the actual muscle contractions \citep{jeannerod:1995_mental,jeannerod:2003_mechanism}. There is also independent evidence that the representations underpinning imagining acting have the same format as those involved in actually acting. This evidence takes the form of similarities in processing profiles. Just as some similarities between imagining seeing something and actually seeing something can be explained on the hypothesis that the representations involved in imagining seeing and actually seeing have a common format \citep{kosslyn:1994_image}, so also some similarities between imagining grasping a cup and actually grasping it are evidence that the representations involved in imagining grasping are of the same format as those involved in actually grasping the cup. We can conclude, then, that imagining and executing actions are both underpinned by motor representations, and that motor representations differ in format from representations involved in both seeing and imagining seeing.

So far we have been arguing that motor and visual representations differ in format.  Why suppose that motor representations also differ in format from intentions?  As we noted earlier, the format of a representation constrains its possible contents. Just as a representation's having a cartographic format restricts its possible contents, so the motor format would imply restrictions on representations having it. In imagining executing actions such as grasping a cup, there are bio-mechanical, dynamical and postural constraints, among others, on what can be imagined. These constraints are closely related to those which govern actually performing such actions \citep{Jeannerod:2001yb}. Such constraints are plausibly explained by the representational format of motor representations. Since no such constraints would be expected to apply where propositional representations are involved, we can conclude (as is widely assumed) that the format of motor representations is not propositional.

@@

The idea that some demonstrative concepts refer to actions by deferring to motor representations immediately raises a question. Could a demonstrative concept really defer to a motor representation? It seems clear that we can't select a motor representation to defer to in the same way that we can select a map when we say `Follow this route!'. After all, motor representations are not things we can point to with our hands. Nevertheless, it does seem that motor representations are available in some sense. To start with an analogy, consider pantomiming an action to yourself. You are rehearsing part of an operation which involves precisely grasping a delicate structure with some tweezers. Just as someone might point to a map and say `Follow that route!', so also they could point to your pantomime and say `Do that!'. In our analogy, the pantomime stands in for a motor representation of the action.  The demonstrative in `Do that!' refers to an action by deferring to the pantomime. Of course this analogy doesn't show that demonstrative concepts can defer to motor representations (at least not unless pantomimes are motor representations of actions). But now consider purely mental pantomime---that is, motor imagery. One might use motor imagery to explore different ways of completing a task and then, having hit on a good solution, think to oneself `Do that!' It seems possible that in some such cases the demonstrative refers by deferring to a motor representation of action involved in mental motor imagery.

But is this really possible? Someone might object that in appealing to motor imagery we are sneaking intentions in through the back door. How can we be sure that it is ever really a motor representation rather than an intention that one defers to in thinking `Do that!'?  Contrast two cases of motor imagery, both involving a tool. In the first case, imagine grasping an object with the tool; and in the second case, imagine releasing the same object with the tool. The two cases involve different imagery. But in what does this difference consist? Could it be a difference in intention that explains how the two cases of motor imagery differ?  Since it is possible to grasp without intentionally grasping, it is surely also possible to imagine grasping without imagining intentionally grasping.  And note that to imagine grasping without imagining intentionally grasping does not necessarily require one to imagine non-intentionally grasping. (It is easy to miss this point by confusing it with the issue of whether the imagining must itself be intentional. Whether or not it is possible to imagine grasping or releasing without \emph{intending to imagine} so acting, one can certainly imagine grasping or releasing without \emph{imagining intentionally} so acting.) So to rule out the possibility that the two cases of motor imagery differ with respect to intention, let the motor imagery be neutral with respect to intention. Is the difference between the two cases then due to differing movements or patterns of muscle contraction? To rule this possibility out, let the movements and muscle contractions involved in both cases be as similar as possible: let the difference between grasping and releasing the object be a matter of how the tool is configured rather than of how your body moves. With the contrast cases elaborated by these two stipulations, it is plausible that the difference in imagery between the two cases will be due to the different motor representations involved in grasping and releasing. So in these cases, the thought `Do that!' will refer to grasping (or releasing) by deferring to a motor image of grasping (or of releasing). Since motor images are a species of motor representation, it follows that demonstrative concepts can refer to actions by deferring to motor representations.

So far we have focused on motor imagery. We are not committed to claiming that demonstrative concepts can only refer to actions by deferring to motor images. Given the parallels between motor imagery and motor preparation \citep{Jeannerod:2001yb}, it is plausible that motor representations feature in experiences of action in such a way that motor actions are available for demonstrative reference. If so, the possibility of demonstrative concepts which refer to actions by deferring to motor representations is supported not just by motor imagery but also by experiences associated with motor activity more generally.

@@

Or is it? So far we have not distinguished between two aspects of action outcomes.  Action outcomes often specify both a way of acting---whether to grasp or release, say---and also what to act on---on the mug or the pen, say.  Since we have been focusing on ways of acting rather than on what is to be acted on, it would be consistent with our arguments to accept that there are demonstrative concepts of ways of acting (such as grasping and reaching, perhaps) which defer by referring to motor representations while denying that any such demonstrative concepts are also about what is to be acted on. If this combination of views were correct, we would have only a partial solution to the interface problem. We would only have explained how the outcomes variously specified by intentions and motor representations non-accidentally match with respect to ways of acting, not with respect to what is to be acted on. However a range of behavioural and neurophysiological evidence shows that motor representations represent not only ways of acting but also objects on which actions might be performed and some of their features related to possible action outcomes involving them (for a review see \citealp{Gallese:2011uq}; for discussion see \citealp[pp.\ 410-3]{pacherie:2000_content}). For example visually encountering a mug sometimes involves representing features such as the orientation and shape of its handle in motor terms \citep{buccino:2009_broken,costantini:2010_where,cardellicchio:2011_space,Tucker:1998,tucker:2001_potentiation}. Reference by deference to motor representation could therefore explain how action outcomes match with respect not only to ways of acting but also with respect to what is to be acted on.\footnote{ In fact, there may be another way of explaining non-accidental matching with respect to what is to be acted on due to \citet[pp.\ 36-8, 44-5, 48-57]{Campbell:2002ge}. In outline, Campbell's idea is to note that intentions can refer to objects by means of perceptual demonstrative elements, and that perceptual and motor representations of objects may be sufficiently commensurate for a perceptually represented object to be reliably selected as a target for motor processes.  It would be consistent to hold both that a view like Campbell's correctly explains non-accidental matching of action outcomes with respect to what is to be acted on, and also that non-accidental matching with respect to ways of acting is explained by demonstrative action concepts which defer to motor representations. We shall leave open the question of whether non-accidental matching involves elements additional to those involved in the view we have been developing.  Our claim is just that a solution to the interface problem need not involve anything other than components of intentions which refer to actions by deferring to motor representations of action outcomes.}

>>>>

\def \ititle {Intention and motor representation in explaining action}
\def \isubtitle {}
\def \iauthor {S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

\section{A motor format for representation}
The second temptation is to suppose that motor representation, or some species of it, is a variety of intention, where intention is understood in the standard way as a propositional attitude with a characteristic role in practical reasoning \citep{Bratman:1987xw}. In this section we explain why this temptation should also be resisted.

As background we first need a generic distinction between content and format. Imagine you are in an unfamiliar city and are trying to get to the central station. A stranger offers you two routes. Each route could be represented by a distinct line on a paper map. The difference between the two lines is a difference in content. Each of the routes could alternatively have been represented by a distinct series of instructions written on the same piece of paper; these cartographic and propositional representations differ in format. The format of a representation constrains its possible contents. For example, a representation with a cartographic format cannot represent what is represented by sentences such as `There could not be a mountain whose summit is inaccessible.'\footnote{Note that the distinction between content and format is orthogonal to issues about representational medium. The maps in our illustration may be paper map or electronic maps, and the instructions may be spoken, signed or written. This difference is one of medium.} The distinction between content and format is necessary because, as our illustration shows, each can be varied independently of the other.

Our aim in this section is to show that motor representations differ from intentions with respect to their format. This is why the second temptation must be resisted. That motor representations differ in format from intentions shows that they are genuinely distinct phenomena.\footnote{ Readers already convinced that motor representation differs from intention in being non-conceptual will not need the following argument in order to conclude that they are distinct phenomena. However the following considerations also indicate that motor and perceptual representations differ in format, which will be relevant later when we consider how motor representations and intentions jointly lead to action.}

How in general can we identify or distinguish representational formats? Because a representational format is typically associated with characteristic performance profiles, it is sometimes possible to infer similarities and differences in representational format from similarities and differences in the processes in which representations feature. This works both for artefactual and mental representations.  To illustrate in terms of our earlier example, suppose that two people have representations of the same route but for one person the route is represented by a line on a map (so in a cartographic format) whereas the other person has a propositional representation of the route. Some transformations are likely to be easier for the person with the cartographic route representation (depending on the projection used, of course); examples include reversing the route, determining how many times a certain river is crossed and transforming the route into a sequence of compass bearings. Other transformations, such as turning the route into a list of salient landmarks, may be easier for the person with the propositional route description. So some patterns of difference in the two people's performances may be explained by the difference in the formats of their representations. If we did not already know that the two people's route representations involved different formats, we might infer this from the facility with which each performed various transformations of the route.

Cognitive neuroscience frequently depends on inferences of just this type. To illustrate, compare imagining seeing an object moving and with actually seeing it move. For this comparison we need to distinguish two ways of imagining seeing. There is a way of imagining seeing which phenomenologically is something like seeing except that it does not necessarily involve being receptive to stimuli. This way of imagining seeing, sometimes called 'sensory imagining', is commonly distinguished from cognitive ways of imagining seeing which might for example involve thinking about seeing \citep[§2.1]{Gendler:2011_imagination}.%
\footnote{Note that we define sensory imagining in terms of phenomenology and make no stipulations about the processes and representations involved.  This is essential for our purposes, since we wish to consider how evidence bears on a conjecture about the format of representations involved in sensory imagining.}
It is sensorily imagining seeing an object move that we wish to compare with actually seeing an object move.  These two have similarities in characteristic performance profile.  For instance, whether an object can be seen all at once depends on its size and distance from the perceiver; strikingly, when subjects imagine seeing an object, whether they can imagine seeing it all at once depends in the same way on size and distance (\citealp{kosslyn:1978_measuring}; \citealp[p.\ 99ff]{kosslyn:1994_image}.  Also, how long it takes to imagine looking over an object depends on the object's subjective size in the same way that how long it would take to actually look over that object would depend on its subjective size \citep{kosslyn:1978_visual}.%
\footnote{These and further examples are discussed by \citet[p.\ 165]{currie:1997_mental}.} Further, imagining seeing something (for example, imagining seeing a visual mask) can modulate and interfere with actually seeing in much the way that actually seeing the thing imagined would \citep{pearson:2008_functional,ishai:1995_common}. The similarities in characteristic performance profile and the particular patterns of interference are good (if non-decisive) reasons to conjecture that imagining seeing and actually seeing involve representations with a common format.  This conjecture is indirectly supported by evidence that sensorily imagining seeing and actually seeing not only have a common neural basis but also involve similar patterns of cortical activation \citep[e.g.][]{page:2011_erp}.

Let us turn to motor representation. Compare imagining moving a ball with actually moving a ball.  To fully specify the comparison we intend, it is again necessary to distinguish two ways of imagining. One way of imagining action is phenomenologically something like acting except that such imaginings are not necessarily responsive to the features of actual objects and do not necessarily result in bodily movements. To illustrate suppose you are about to dive into a pool and, standing at the edge, mentally pantomime launching yourself from the bank. Some phenomenal characteristics of this imaginative exercise may be barely distinguishable from some of those associated with actually launching yourself into the pool. This way of imagining action can be distinguished from cognitive ways of imagining action which might involve thinking about an action.%
\footnote{
On distinguishing these two ways of imagining action, see \citet[p.\ 161]{currie:1997_mental}, \citet[p.\ 727]{jeannerod:1995_mental}, and \citet[p.\ 638-9]{kosslyn:2001_neural}. The former, phenomenologically action-like imagining is sometimes labelled 'motor' or 'internal' and occasionally identified by its links to motor processes or by features of the format or content of the representations involved (\citealp[p.\ 1400]{annett:1995_motor}). We avoid these labels because we introduce the distinction by appeal to phenomenology only and do not stipulate that motor representations are involved. It is essential for what follows that the involvement of motor representations in the phenomenologically action-like way of imagining action is a discovery rather than a terminological stipulation.}
%
The comparison we intend is between imagining moving a ball in the former, phenomenologically-action like way and actually moving a ball. There is evidence that the way imagining performing an action unfolds in time is similar in some respects to the way actually performing an action of the same type would unfold.  For instance, how long it takes to imagine moving an object is closely related to how long it would take to actually move that object \citep{decety:1989_timing, decety:1996_imagined, Jeannerod:1994oz}. In addition, for actions such as grasping the handle of a cup, manipulating the target object in ways that make the action harder (such as orienting the cup's handle to make it less convenient for you to grasp) make a corresponding difference to the effort involved in imagining performing the action \citep{parsons:1994_temporal, frak:2001_orientation}. Further, imagining performing an action can selectively interfere with performance of a related action. For example, suppose you are faced with an array of objects one of which---the target---you will shortly be required to grasp.  Subjects who imagine grasping an object other than the target object tend to be slower in subsequently grasping the target object than subjects who do not imagine acting or subjects who imagine grasping the target object \citep{ramsey:2010_incongruent_}. Just as the similarities between imagining seeing and actually seeing are evidence for the hypothesis that the representations involved in imagining seeing and actually seeing have a common format, so also the similarities in characteristic performance profile between imagining acting and actually acting, together with the particular patterns of interference between the two, suggest that imagining acting and actually acting involve a common representational format. And much as in the case of seeing and imagining seeing, acting and imagining acting involve many of the same processes almost up to the actual muscle contractions \citep{jeannerod:1995_mental, jeannerod:2003_mechanism}.

The fact that motor representation is involved in one way of imagining acting means that we can use imagining acting to investigate the format of motor representations. This enables us to examine characteristics of processes involving motor representation which are not directly consequences of an agent's actual body or actual environment.

Differences in performance provide reasons to distinguish the formats of visual and motor representations. To see why, consider two tasks involving mental rotation. Judging the laterality of a rotated letter is thought to involve the phenomenologically seeing-like form of imagination \citep{jordan:2001_cortical}, whereas judging the laterality of a rotated hand is thought to involve the phenomenologically action-like form of imagination \citep{parsons:1987_imagined, gentilucci:1998_right}. Ordinary subjects who are asked to judge the laterality of a hand rotated to various degrees are slower and less accurate when the hand's position is maximally biomechanically awkward, when the hand is rotated so that the middle finger points downwards. By contrast, no such effect occurs for comparable tasks involving letters rather than hands. Can this difference in performance in imagining hands and letters be entirely explained by a difference in what is imagined (hands vs. letters)? There are subjects who can perform both tasks but whose performance is not different for hands and letters \citep{Fiori:2012fk}. These are subjects suffering Amyotrophic Lateral Sclerosis (ALS), which impairs motor representation \citep{parsons:1998_cerebrally}. If the hand-letter difference in performance were entirely explained by a difference in what is imagined, we would expect ALS and ordinary subjects to exhibit the same difference in performance since both are imagining hands and letters. But this is not the case. So some differences in performance linked to visual and motor representation cannot be entirely explained by differences in content.  This suggests that the differences in performance are explained by a difference in format.

Given that we need to posit differences in the formats of motor and visual representations in order to explain performance differences in mental rotation, it is plausible that these differences in format also explain some of the differences in performance linked to the timing of, and effort required for, imagining acting and imagining seeing.  For instance, contrast imagining rotating a ball with imagining seeing a ball rotating.%
\footnote{It may be difficult in practice to imagine acting without also imagining seeing, and conversely; it may also sometimes be difficult to distinguish imagine acting from imagining seeing \citep[as][p.\ 170 note]{currie:1997_mental}. However ordinary subjects can separate the two well enough to confirm predictions about their differences \citep[see, e.g.,][]{kosslyn:2001_imagining}.
}
As already mentioned, how quickly the former can be done is a function of how long it would take the agent to rotate the ball, whereas how quickly the latter can be done depends on how rapidly the ball can rotate and still be perceived as rotating. Similarly, we mentioned that factors making actually acting more effortful also make imagining acting more effortful: such factors are unlikely to affect the effort involved in imagining seeing. The explanation for these differences between imagining acting and imagining seeing plausibly involves a difference in the formats of the representations involved. That the two involve different representational formats is consistent with evidence that these two imaginings also involve different processes \citep{kosslyn:2001_imagining}. For instance, each can be selectively impaired \citep{sirigu:2011_motor}; and factors such as limb amputation or hand posture can interfere with imagining acting without interfering with  imagining seeing \citep{nico:2004_left, vargas:2004s_influence,  fourkas:2006_influence}.

So far we have been arguing that motor and visual representations differ in format.  Why suppose that motor representations also differ in format from intentions?  Contrast two ways of imagining taking a shot in basketball, one involving the phenomenologically action-like kind of imagination and the other involving a cognitive kind of imagination.  The contrast we require is roughly between the way a former player might imagine this and the way that someone who has only ever read about basketball might imagine it.  As we have seen, the way the phenomenologically action-like kind of imagination unfolds in time and the amount of effort it involves will depend on bio-mechanical, dynamical and postural constraints, among others. These constraints are closely related to those which govern actually performing such actions \citep{Jeannerod:2001yb}, and some can be altered by acquiring or losing motor expertise.  By contrast no such constraints would be expected always to apply where a cognitive kind of imagination is involved.  In line with the general strategy of inferring differences in format from differences in characteristic performance profile, we conclude that motor representations differ in format from those involved in cognitive kinds of imagination, which are plausibly propositional.

But are we too hasty in concluding that motor and propositional representations differ in format?  It might be objected that their characteristic performance profiles are not so different, for in cognitive imagination the fact that an agent is imagining herself acting will mean that how she imagines the action unfolding will reflect constraints on what she can do. But while this will sometimes be the case, a cognitive kind of imagining need not involve imagining an action unfolding in a way consistent with one's actual abilities. What distinguishes the phenomenologically action-like form of imagination is that some bio-mechanical, dynamical and postural constraints are inescapable.  To make this vivid consider imagining reaching for a distant object.  If the object is manifestly far out of reach it will not normally be possible to do this using the phenomenologically action-like kind of imagination, whereas no such difficulty need occur where a cognitive kind of imagination is involved.  After all, where a cognitive kind of imagination is involved one can imagine having much longer limbs (or an entirely different body) whereas this cannot be achieved at will where the phenomenologically action-like kind of imagination is involved.  Finally, where there are constraints on a cognitive kind of imagination these are generally mediated by beliefs or suppositions about one's own abilities; it seems unlikely that this is true of the phenomenologically action-like kind of imagination.

@@

The idea that some demonstrative concepts refer to actions by deferring to motor representations immediately raises a question. Could a demonstrative concept really defer to a motor representation? It seems clear that we can't select a motor representation to defer to in the same way that we can select a map when we say `Follow this route!'. After all, motor representations are not things we can point to with our hands. Nevertheless, it does seem that motor representations are available in some sense. To start with an analogy, consider pantomiming an action to yourself. You are rehearsing part of an operation which involves precisely grasping a delicate structure with some tweezers. Just as someone might point to a map and say `Follow that route!', so also they could point to your pantomime and say `Do that!'. In our analogy, the pantomime stands in for a motor representation of the action.  The demonstrative in `Do that!' refers to an action by deferring to the pantomime. Of course this analogy doesn't show that demonstrative concepts can defer to motor representations (at least not unless pantomimes are motor representations of actions). But now consider purely mental pantomime---that is, the phenomenologically-action like kind of imagination. One might use this kind of imagination to explore different ways of completing a task and then, having hit on a good solution, think to oneself `Do that!' It seems possible that in some such cases the demonstrative refers by deferring to a motor representation of action involved in imagining acting.

But is this really possible? Someone might object that in appealing to imagining acting we are sneaking intentions in through the back door. How can we be sure that it is ever really a motor representation rather than an intention that one defers to in thinking `Do that!'?  Contrast two cases of imagining acting, both involving a tool. In the first case, imagine grasping an object with the tool; and in the second case, imagine releasing the same object with the tool. The two cases are different but in what does their difference consist? Could it be a difference in intention that explains how they differ?  Since it is possible to grasp without intentionally grasping, it is surely also possible to imagine grasping without imagining intentionally grasping.  And note that to imagine grasping without imagining intentionally grasping does not necessarily require one to imagine non-intentionally grasping. (It is easy to miss this point by confusing it with the issue of whether the imagining must itself be intentional. Whether or not it is possible to imagine grasping or releasing without \emph{intending to imagine} so acting, one can certainly imagine grasping or releasing without \emph{imagining intentionally} so acting.) So to rule out the possibility that the two imaginings differ with respect to intention, let both be neutral with respect to intention. Is the difference between the two cases then due to differing movements or patterns of muscle contraction? To rule this possibility out, let the movements and muscle contractions involved in both cases be as similar as possible: let the difference between grasping and releasing the object be a matter of how the tool is configured rather than of how your body moves. With the contrast cases elaborated by these two stipulations, it is plausible that the difference between the two imaginings will be due to the different motor representations involved in grasping and releasing. So in these cases, the thought `Do that!' will refer to grasping (or releasing) by deferring to a motor representation of grasping (or of releasing). It follows that demonstrative concepts can refer to actions by deferring to motor representations.

So far we have focused on imagining acting. We are not committed to claiming that demonstrative concepts can only refer to actions by deferring to motor representations involved in imagination. Given the parallels between the phenomenologically action-like kind of imagination and motor preparation \citep{Jeannerod:2001yb}, it is plausible that motor representations feature in experiences of action in such a way that motor actions are available for demonstrative reference. If so, the possibility of demonstrative concepts which refer to actions by deferring to motor representations is supported not just by experiences associated with imagining acting but also by experiences associated with actually acting.

But how do demonstrative concepts feature in practical reasoning, which does not appear always to involve imagining or experiencing acting?  Our proposal is similar to what one might say about demonstrative route concepts.  Someone encounters a map with a route marked on it.  Her experience of this route is necessary for her to acquire a demonstrative concept which refers to the route by deferring to the cartographic representation of it.  But once she has this demonstrative concept, she can use it on future occasions without fresh experiences of the route (although there may be some dependence on memory); and her use of this concept does not depend on the continued existence of the original representation of the route.  Similarly, on our view experience of action is necessary for the acquisition of demonstrative concepts of action such as concepts of grasping and reaching but, perhaps subject to requirements on memory, not for their continued use in practical thought.

@@

Or is it? So far we have not distinguished between two aspects of action outcomes.  Action outcomes often specify both a way of acting---whether to grasp or release, say---and also what to act on---on the mug or the pen, say.  Since we have been focusing on ways of acting rather than on what is to be acted on, it would be consistent with our arguments to accept that there are demonstrative concepts of ways of acting (such as grasping and reaching, perhaps) which defer by referring to motor representations while denying that any such demonstrative concepts are also about what is to be acted on. If this combination of views were correct, we would have only a partial solution to the interface problem. We would only have explained how the outcomes variously specified by intentions and motor representations non-accidentally match with respect to ways of acting, not with respect to what is to be acted on. However a range of behavioural and neurophysiological evidence shows that motor representations represent not only ways of acting but also objects on which actions might be performed and some of their features related to possible action outcomes involving them (for a review see \citealp{Gallese:2011uq}; for discussion see \citealp[pp.\ 410-3]{pacherie:2000_content}). For example visually encountering a mug sometimes involves representing features such as the orientation and shape of its handle in motor terms \citep{buccino:2009_broken,costantini:2010_where,cardellicchio:2011_space,Tucker:1998,tucker:2001_potentiation}. Reference by deference to motor representation could therefore explain how action outcomes match with respect not only to ways of acting but also with respect to what is to be acted on.%
\footnote{ In fact, there may be another way of explaining non-accidental matching with respect to what is to be acted on due to \citet[pp.\ 36-8, 44-5, 48-57]{Campbell:2002ge}. In outline, Campbell's idea is to note that intentions can refer to objects by means of perceptual demonstrative elements, and that perceptual and motor representations of objects may be sufficiently commensurate for a perceptually represented object to be reliably selected as a target for motor processes.  It would be consistent to hold both that a view like Campbell's correctly explains non-accidental matching of action outcomes with respect to what is to be acted on, and also that non-accidental matching with respect to ways of acting is explained by demonstrative action concepts which defer to motor representations. We shall leave open the question of whether non-accidental matching involves elements additional to those involved in the view we have been developing.  Our claim is just that a solution to the interface problem need not involve anything other than components of intentions which refer to actions by deferring to motor representations of action outcomes.
}

At this point we should acknowledge a complication.  Reference by deference to motor representation depends on motor experience.  Above we suggested that motor experience is needed for the acquisition of demonstrative concepts of ways of acting but not for the continued use of such concepts in practical reasoning.  However, things are more complicated where constituents of intentions refer to particular things to be acted on.  Agents will not always have experienced these things in the past.  Accordingly fully resolving the interface problem by appeal to demonstratives requires that motor representations of particular things are generally associated with experiences of those things.  When we spontaneously intend to act on an object we have no previous experience of, our experience of that object would need to have motor as well as perhaps visual, tactile or acoustic aspects.  There is indeed some evidence for the ubiquity of motor aspects of experience (and also evidence that motor representation does not always modulate how objects are experienced, but that is not relevant here).  For example, temporarily changing subjects' motor abilities by artificially extending their reach systematically affects their judgements of how far away objects are \citep{linkenauger:2009_effects, costantini2011tool}. Given that such judgements are based on experience,\footnote{
It may be objected that these judgements could reflect non-perceptual expectations; \citet[pp.\ 203-4]{witt:2011_action} review evidence against this possibility.} 
this illustrates one way in which experience may be shaped in part by motor representation of objects.  There is also evidence that perceived size can be influenced by ability \citep[e.g.][]{witt2009kicking}.  In short, then, it is plausible that motor representation of objects modulates experiences of them.  This indicates that it may be possible to refer not only to ways of acting by also to what to act on by deferring to motor representations.
